Combining formal and distributional models of predicate semantics

### 2016-03-15 papers/acl2016/paper.tex
minor edits
Former-commit-id: b1b122922830ecb6ffff8a0e9acf97291dea192b

Krishnamurthy and
Mitchell~\shortcite{krishnamurthy-2015-semparse-open-vocabulary}
provides a partial answer to this question with their open-vocabulary
semantic parser. This system answers compositional, fill-in-the-blank
natural language queries against Freebase, such as ``Hollywood honcho
\blank{},'' using \emph{distributional} models of predicate
semantics. The method semantically parses text to a surface logical
form containing predicates derived from the text itself, such as
$\lambda x.\predicate{honcho}(x) \land
\predicate{honcho\_N/N}(\entity{Hollywood}, x)$, then learns the
denotations of these predicates using distributional information from
a large, entity-linked corpus. This method combines the broad coverage
of distributional approaches with the compositionality of semantic
parsing; however, it does not use structured information from Freebase
to assist with its predictions.

@@

We demonstrate our approach on the task of answering fill-in-the-blank
natural language queries, finding that our approach provides a 62\%
relative improvement in mean average precision over K\&M. (TODO: other
empirical findings?)

>>>>

Krishnamurthy and
Mitchell~\shortcite{krishnamurthy-2015-semparse-open-vocabulary}
provide a partial answer to this question with their open-vocabulary
semantic parser. This system answers compositional, fill-in-the-blank
natural language queries against Freebase, such as ``Hollywood honcho
\blank{},'' using \emph{distributional} models of predicate
semantics. The method semantically parses text to a surface logical
form containing predicates derived from the text itself, such as
$\lambda x.\predicate{honcho}(x) \land
\predicate{honcho\_N/N}(\entity{Hollywood}, x)$, then learns the
denotations of these predicates using distributional information from
a large, entity-linked corpus. This method combines the broad coverage
of distributional approaches with the compositionality of semantic
parsing; however, it does not use structured information from Freebase
to assist with its predictions.

@@

We demonstrate our approach on the task of answering fill-in-the-blank
natural language queries, finding that our approach provides a 62\%
relative improvement in mean average precision over K\&M. (TODO: other
empirical findings? It would be nice to talk about what features get
learned for what words, etc.)
